Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-12 write-ups/PLDI/paper.tex
added a table about the applications

@@

\newcommand{\myfig}{Fig.~}
\newcommand{\myfiglong}{Figure~}
\newcommand{\myfigs}{Figs.~}
\newcommand{\mytab}{Tab.~}
\newcommand{\mytablong}{Table~}
\newcommand{\mysec}{Sec.~}
\newcommand{\myalg}{Alg.~}
\newcommand{\nvidia}{Nvidia\xspace}
\newcommand{\totalcombinations}{70\xspace}
\newcommand{\positivecombinations}{55\xspace}
\newcommand{\cbedot}{\emph{cbe-dot}\xspace}
\newcommand{\cbeht}{\emph{cbe-ht}\xspace}
\newcommand{\ctoctree}{\emph{ct-octree}\xspace}
\newcommand{\tpotm}{\emph{tpo-tm}\xspace}
\newcommand{\sdkred}{\emph{sdk-red}\xspace}
\newcommand{\sdkrednf}{\emph{sdk-red-nf}\xspace}
\newcommand{\lsbh}{\emph{ls-bh}\xspace}
\newcommand{\lsbhnf}{\emph{ls-bh-nf}\xspace}
\newcommand{\cubscan}{\emph{cub-scan}\xspace}
\newcommand{\cubscannf}{\emph{cub-scan-nf}\xspace}
\newcommand{\heuristiccombinations}{eight\xspace}
\newcommand{\effectivethreshold}{5\%\xspace}
\definecolor{Gray}{gray}{0.85}

@@

@@

\ADComment{Give stats on how many variables had to be marked with
  $\transmit$ (i.e., occurred in the restoration context), how many barriers we changed to resizing, how many offer kill and offer fork calls we included.}

>>>>

\newcommand\crule[3][black]{\textcolor{#1}{\rule{#2}{#3}}}

@@

\newcommand{\myfig}{Fig.~}
\newcommand{\myfiglong}{Figure~}
\newcommand{\myfigs}{Figs.~}
\newcommand{\mytab}{Tab.~}
\newcommand{\mytablong}{Table~}
\newcommand{\mysec}{Sec.~}
\newcommand{\myalg}{Alg.~}
\newcommand{\nvidia}{Nvidia\xspace}
\newcommand{\totalcombinations}{70\xspace}
\newcommand{\positivecombinations}{55\xspace}
\newcommand{\cbedot}{\emph{cbe-dot}\xspace}
\newcommand{\cbeht}{\emph{cbe-ht}\xspace}
\newcommand{\ctoctree}{\emph{ct-octree}\xspace}
\newcommand{\tpotm}{\emph{tpo-tm}\xspace}
\newcommand{\sdkred}{\emph{sdk-red}\xspace}
\newcommand{\sdkrednf}{\emph{sdk-red-nf}\xspace}
\newcommand{\lsbh}{\emph{ls-bh}\xspace}
\newcommand{\lsbhnf}{\emph{ls-bh-nf}\xspace}
\newcommand{\cubscan}{\emph{cub-scan}\xspace}
\newcommand{\cubscannf}{\emph{cub-scan-nf}\xspace}
\newcommand{\heuristiccombinations}{eight\xspace}
\newcommand{\effectivethreshold}{5\%\xspace}
\definecolor{Gray3}{gray}{0.9}
\definecolor{Gray2}{gray}{0.75}
\definecolor{Gray1}{gray}{0.6}

@@

\begin{table}
\small
\centering
\begin{tabular}{ l c c c }
app & resizing barriers & ckill - cfork & tranmit vars\\
\hline
\rowcolor{Gray1}
color & 2 / 2 & 0 - 0 & 4\\
\rowcolor{Gray1}
mis & 3 / 3 & 0 - 0 & 0\\
\rowcolor{Gray1}
bc & 3 / 6 & 0 - 0 & 3\\
\rowcolor{Gray1}
p-sssp & 3 / 3 & 0 - 0 & 0 \\
\rowcolor{Gray2}
bfs & 2 / 2 & 0 - 0  & 4 \\
\rowcolor{Gray2}
l-sssp & 2 / 2 & 0 - 0  & 4 \\
\rowcolor{Gray3}
octree & 0 / 0 & 1 - 1 & 0\\
\rowcolor{Gray3}
game & 0 / 0 & 1 - 1 & 0\\
\end{tabular} \\
\vspace{.2cm}
\crule[Gray1]{.2cm}{.2cm} - Pannotia \hspace{.4cm} \crule[Gray2]{.2cm}{.2cm} - Lonestar GPU  \hspace{.4cm}  \crule[Gray3]{.2cm}{.2cm} - work stealing
\caption{Blocking GPU applications investigated}
\label{tab:applications}
\end{table}

@@

\ADComment{Give stats on how many variables had to be marked with
  $\transmit$ (i.e., occurred in the restoration context), how many
  barriers we changed to resizing, how many offer kill and offer fork
  calls we included.}  \TSComment{check out
  Table~\ref{tab:applications}. The barrier column shows how many of
  the original barriers were ported to resizing barriers. In all cases
  except bc we converted all of them. The only reason why bc is
  different is because barriers occur deeper in the call stack and our
  prototype cannot handle that. The algorithm itself is compatable
  (i.e. changing these barriers is as easy as any other, there is
  nothing special about them.)}
